### 2018-11-12 poster-nexus-conference/blocks/conclusions.tex
Add poster

\begin{block}{Key Findings}
    \begin{itemize}
        \item If risk uncertainty increases into future (i.e., \cref{fig:conceptual-sketch}) then adaptation strategies with short $M$ are preferred \cite{Haasnoot:2013im, Zeff:2016hx}
        \item Risk profile of short-$M$ projects dominated by \acrlong{lfv} \cite{Jain:2001hz, Hodgkins:2017hw}
        \item Even though the \gls{hmm} is an imperfect analog for \gls{enso}, it performs well for short $M$
        \item When $M$ is long, trends must be estimated explicitly (but this requires more information -- longer $N$)
        \item Depending on the specific climate mechanisms that impact a particular site, and the predictability thereof, the cost and risk associated with a sequence of short-term adaptation projects may be lower than with building a single, permanent structure to prepare for a worst-case scenario far into the future
    \end{itemize}
\end{block}

>>>>

{   
    \large
    \setbeamercolor*{block body}{fg=black,bg=wcblue!30}
    \begin{block}{Key Findings}
        Depending on the specific climate mechanisms that impact a particular site, and the predictability thereof, the cost and risk associated with a sequence of short-term adaptation projects may be lower than with building a single, permanent structure to prepare for a worst-case scenario far into the future:
        \begin{itemize}
            \item If uncertainty increases into future then adaptation strategies with short planning periods are preferred
            \item Risk profile of short-$M$ projects dominated by \acrlong{lfv} \cite{Jain:2001hz, Hodgkins:2017hw}
            \item Even though the \gls{hmm} is an imperfect analog for \gls{enso}, it performs well for short planning periods
            \item When the planning period is long, trends must be estimated explicitly (requiring more data)
        \end{itemize}
    \end{block}
}

### 2018-11-12 poster-nexus-conference/blocks/systematic-experiments.tex
Add poster

\begin{block}{Experiment Results}
  We evaluate bias and variance as a function of $M$, $N$, and estimation method for three scenarios.
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{secular-only-nino3-bias-variance.pdf}
    \caption{
      Expected estimation bias and variance for sequences with secular change only (no \gls{lfv}).
    }\label{fig:secular-nino3-bias-variance}
  \end{figure}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{lfv-only-nino3-bias-variance.pdf}
    \caption{
      As \cref{fig:secular-nino3-bias-variance} but for sequences generated with zero secular change and \gls{lfv} from the \gls{enso} index.
    }\label{fig:lfv-nino3-bias-variance}
  \end{figure}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{lfv-secular-nino3-bias-variance.pdf}
    \caption{
      As \cref{fig:secular-nino3-bias-variance} but for sequences generated from the NINO3 model with both \gls{lfv} and secular change.
    }\label{fig:lfv-secular-nino3-bias-variance}
  \end{figure}
\end{block}

>>>>

\begin{block}{Experiment Results}
  We evaluate bias and variance as a function of $M$, $N$, and estimation method for three scenarios.
  \begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{secular-only-nino3-bias-variance.pdf}
    \caption{
      Expected estimation bias and variance for sequences with secular change only (no \gls{lfv}).
    }\label{fig:secular-nino3-bias-variance}
  \end{figure}
  \begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{lfv-only-nino3-bias-variance.pdf}
    \caption{
      As \cref{fig:secular-nino3-bias-variance} but for sequences generated with zero secular change and \gls{lfv} from the \gls{enso} index.
    }\label{fig:lfv-nino3-bias-variance}
  \end{figure}
  \begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{lfv-secular-nino3-bias-variance.pdf}
    \caption{
      As \cref{fig:secular-nino3-bias-variance} but for sequences generated from the NINO3 model with both \gls{lfv} and secular change.
    }\label{fig:lfv-secular-nino3-bias-variance}
  \end{figure}
\end{block}
